Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-20 paper.tex
edits inizio Section 4

%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}
\vspace{-0.2cm}
\section{Experiments}\label{sec:experiments}
Experiments are meant to show the effectiveness of the proposed algorithm on real-world sequences, and to specifically assess the advantage of using segmentation for detecting camera displacements. 
\vspace{-0.3cm}
\subsubsection{Considered Methods}
As far as camera-displacement is concerned, Algorithm \eqref{alg:DISPL} is compared against three variants: 1) monitoring the luma on the whole image (\emph{Luma-Total}), 2) monitoring the total energy of the difference between two adjacent frames (\emph{Frame Difference}), and 3) monitoring the luma on $K$ regions obtained by clustering $[r(x), c(x)]$, which yields a Voronoi partitioning of the scene (\emph{Luma-Voronoi}). Frame difference is considered as a baseline technique for displacement detection, while comparison against \emph{Luma-Voronoi} shows the advantages of setting regions depending of the image content. \\
In the experiments on blurring detection, we compare Algorithm \ref{alg:DISPL} (where $\partial g$ is monitored on the whole image), against monitoring $\partial g$ separately in image regions, as done for $\partial l_k$.
\vspace{-0.3cm}
\subsubsection{Datasets}
The considered dataset contains  sequences of  frames taken from webcams monitoring urban areas (e.g., see Figure \ref{fig:sequences}(a)), in which we've taken the central crop of each image (about $3/4$ of the original image). 
%The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module. 
In order to have a wide and sound dataset, the tampering events have been made synthetically, blurring the frames by gaussian kernels (see, Figure \ref{fig:sequences}(b)) or moving the crop of the frames in order to simulate displacements (see Figure \ref{fig:sequences}(c)). 
%Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
%In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens. 
At last we have considered $8$ different scenarios, for a total of $24410$ frames considered, in which we've inserted $5\%$ of displacement events ($1224$ frames) and $5\%$ of blurring events ($1224$ frames).\footnote{Sequences can be released upon request}
\vspace{-0.3cm}
\subsubsection{Performance Assessment}
The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values. In particular, each point in the ROC curve depicts a pair of values (1-SPECIFICITY, RECALL) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP, FP, TN, FN represent the number of true positives (tampered frames correctly detected), of false positives (tampering-free frames detected), of true negatives (tampering-free frames not detected) and of false negatives (missed tampered frames), respectively, for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves and the Area Under the Curve (AUC) reported in Figure~\ref{fig:ROCdisplacement} and its caption indicate that camera displacements can be effectively detected by all the considered methods, and that Algorithm~\ref{alg:DISPL} achieves the best performance (the \emph{Frame-Difference} curve has not been reported because it was quite below the others). This result suggests that separately monitoring the luma over image regions is an effective strategy and that the regions have to be suitably estimated. For the visualization sake, these ROC curves have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms. We observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.3\%$ of false alarms, which is half of the whole image solution ($0.7\%$) and less than one third of the Voronoi solution ($1\%$). Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.

>>>>

%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}
\vspace{-0.2cm}
\section{Experiments}\label{sec:experiments}
Experiments are meant to assess the advantages of using a segmentation in a tampering-detection framework like Algorithm~\eqref{alg:DISPL}. In particular, to assess the importance of partitioning the scene we compare Algorithm~\eqref{alg:DISPL} against a solution monitoring the indicators on the whole image (\emph{Total} in Figure~\ref{fig:ROC}). To show that regions have to be defined depending on the image content, we consider also Algorithm~\eqref{alg:DISPL} when the $K$ regions are obtained by clustering $[r(x), c(x)]$, which yields a Voronoi partitioning of the scene (\emph{Voronoi} in Figure~\ref{fig:ROC}). For both regions defined as in Section~\ref{subsec:Segmentation} and Voronoi regions, we test the two extreme cases where $\Gamma_l = 1$ and $\Gamma_l = K-1$ ($\Gamma_d = 1$ and $\Gamma_d = K-1$).

\subsubsection{Datasets}
We recorded $8$ sequences from webcams monitoring different urban areas and we synthetically introduced $5\%$ of tampered frames in each. In each sequence we have cropped the central region, removing 50 rows from the top and bottom, and 50 columns from the left and right of the image. Blurring was obtained by convolution against a Gaussian kernels (as in Figure \ref{fig:sequences}(a)), while displacements were simulated by moving the central cropping regions of a random shift between 20 and 50 pixels in each direction (see Figure \ref{fig:sequences}(b)).  Overall, the dataset contains $24410$ frames, in which we've inserted $5\%$ of displacement events ($1224$ frames) and $5\%$ of blurring events ($1224$ frames).\footnote{Sequences can be released upon request.}
\gi{image sizes? blur kernel? quanti pixel il displacemnet?}
%The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module.

%Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
%In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens. 
\vspace{-0.3cm}
\subsubsection{Performance Assessment}
The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values. In particular, each point in the ROC curve depicts a pair of values (1-SPECIFICITY, RECALL) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP, FP, TN, FN represent the number of true positives (tampered frames correctly detected), of false positives (tampering-free frames detected), of true negatives (tampering-free frames not detected) and of false negatives (missed tampered frames), respectively, for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves and the Area Under the Curve (AUC) reported in Figure~\ref{fig:ROCdisplacement} and its caption indicate that camera displacements can be effectively detected by all the considered methods, and that Algorithm~\ref{alg:DISPL} achieves the best performance (the \emph{Frame-Difference} curve has not been reported because it was quite below the others). This result suggests that separately monitoring the luma over image regions is an effective strategy and that the regions have to be suitably estimated. For the visualization sake, these ROC curves have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms. We observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.3\%$ of false alarms, which is half of the whole image solution ($0.7\%$) and less than one third of the Voronoi solution ($1\%$). Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.
